---
output: bd::html_body
---

```{r, echo=FALSE, message=FALSE, warning=FALSE}
source("preamble.R")
```

## Estimate true prevalence from individuals samples

### Description

Bayesian estimation of true prevalence from apparent prevalence obtained by testing individual samples.

### Usage

```{r, eval=FALSE}
truePrev(x, n, SE = 1, SP = 1, prior = c(1, 1),
         nchains = 2, burnin = 10000, update = 10000,
         verbose = FALSE)
```

### Arguments

<table>
 <tr>
  <td>`x`</td>
  <td>The apparent number of positive samples</td>
 </tr>
 <tr>
  <td>`n`</td>
  <td>The sample size</td>
 </tr>
 <tr>
  <td>`SE, SP`</td>
  <td>The prior distribution for sensitivity (SE) and specificity (SP); see [details](#details) for specification of these distributions</td>
 </tr>
 <tr>
  <td>`prior`</td>
  <td>The parameters of the prior Beta distribution for true prevalence; defaults to `c(1, 1)`</td>
 </tr>
 <tr>
  <td>`nchains`</td>
  <td>The number of chains used in the estimation process; must be \le 2</td>
 </tr>
 <tr>
  <td>`burnin`</td>
  <td>The number of discarded model iterations; defaults to 10,000</td>
 </tr>
 <tr>
  <td>`update`</td>
  <td>The number of withheld model iterations; defaults to 10,000</td>
 </tr>
 <tr>
  <td>`verbose`</td>
  <td>Logical flag, indicating if JAGS process output should be printed to the R console; defaults to `FALSE`</td>
 </tr>
</table>

### Details

`truePrev` calls on [**JAGS**](http://mcmc-jags.sourceforge.net/) via the [**rjags**](https://cran.r-project.org/package=rjags) package to estimate the true prevalence from the apparent prevalence in a Bayesian framework. The default model, in BUGS language, is given below. To see the actual fitted model, see the model slot of the [`prev`-object](?main=docs&sub=prev-class).

```{r, eval=FALSE}
model {
  x ~ dbin(AP, n)
  AP <- SE * TP + (1 - SP) * (1 - TP)
  # SE ~ user-defined
  # SP ~ user-defined
  TP ~ dbeta(prior[1], prior[2])
}
```

The test sensitivity (`SE`) and specificity (`SP`) can be specified, independently, as one of `fixed` (default), `uniform`, `beta`, `pert`, or `beta-expert`.

More info on specifying distributions is available [here](?main=docs&sub=distributions).

### Value

A `r doc("prev-class")` object.

### Note

Markov chain Monte Carlo sampling in `truePrev` is performed by [**JAGS**](http://mcmc-jags.sourceforge.net/) (Just Another Gibbs Sampler) through the [**rjags**](https://cran.r-project.org/package=rjags) package. JAGS can be downloaded from http://sourceforge.net/projects/mcmc-jags/.

### References

* Speybroeck N, Devleesschauwer B, Joseph L, Berkvens D (2013) Misclassification errors in prevalence estimation: Bayesian handling with care. _Int J Public Health_ **58**:791-795. http://dx.doi.org/10.1007/s00038-012-0439-9
* Online Shiny application: http://prevalence.cbra.be/truePrev

### See also

[**coda**](https://cran.r-project.org/package=coda) for various functions that can be applied to the `prev@mcmc` object

`r doc("truePrevPools")`: estimate true prevalence from apparent prevalence obtained by testing _pooled_ samples with a single test

`r doc("truePrevMulti")`: estimate true prevalence from apparent prevalence obtained by testing _individual_ samples with multiple tests, using a conditional probability scheme

`r doc("truePrevMulti2")`: estimate true prevalence from apparent prevalence obtained by testing _individual_ samples with multiple tests, using a covariance scheme

`r doc("betaPERT")`: calculate the parameters of a Beta-PERT distribution

`r doc("betaExpert")`: calculate the parameters of a Beta distribution based on expert opinion

### Examples

```{r}
## Taenia solium cysticercosis in Nepal
## 142 positives out of 742 pigs sampled
```

```{r}
## Model SE and SP based on literature data
## Sensitivity ranges uniformly between 60% and 100%
## Specificity ranges uniformly between 75% and 100%
```

```{r}
## .. BUGS-style
truePrev(x = 142, n = 742,
         SE = ~dunif(0.60, 1.00), SP = ~dunif(0.75, 1.00))
```

```{r}
## .. list-style
SE <- list(dist = "uniform", min = 0.60, max = 1.00)
SP <- list(dist = "uniform", min = 0.75, max = 1.00)
truePrev(x = 142, n = 742, SE = SE, SP = SP)
```

```{r}
## Model SE and SP based on expert opinion
## .. SE lies in between 60% and 100%; most likely value is 90%
## .. SP is with 95% confidence larger than 75%; most likely value is 90%
SE <- list(dist = "pert", a = 0.60, m = 0.90, b = 1.00)
SP <- list(dist = "beta-expert", mode = 0.90, lower = 0.75, p = 0.95)
truePrev(x = 142, n = 742, SE = SE, SP = SP)
```

```{r}
## Model SE and SP as fixed values (each 90%)
truePrev(x = 142, n = 742, SE = 0.90, SP = 0.90)
```

### Tutorials

* [Estimating true prevalence based on a single test](?main=tutorials)

```{r child="footer.Rmd"}
```
