---
output: bd::html_body
---

```{r, echo=FALSE, message=FALSE, warning=FALSE}
source("preamble.R")
```

## Estimate true prevalence from pooled samples

### Description

Bayesian estimation of true prevalence from apparent prevalence obtained by testing _pooled_ samples.

### Usage

```{r, eval=FALSE}
truePrevPools(x, n, SE = 1, SP = 1, prior = c(1, 1),
              nchains = 2, burnin = 10000, update = 10000,
              verbose = FALSE)
```

### Arguments

<table>
<tbody>
 <tr valign="top">
  <td>`x`</td>
  <td>The vector of indicator variables, indicating whether a pool was positive (`"1"`) or negative (`"0"`)</td>
 </tr>
 <tr valign="top">
  <td>`n`</td>
  <td>The vector of pool sizes</td>
 </tr>
 <tr valign="top">
  <td>`SE, SP`</td>
  <td>The prior distribution for sensitivity (SE) and specificity (SP); see 'Details' below for specification of these distributions</td>
 </tr>
 <tr valign="top">
  <td>`prior`</td>
  <td>The parameters of the prior Beta distribution for true prevalence; defaults to `c(1, 1)`</td>
 </tr>
 <tr valign="top">
  <td>`nchains`</td>
  <td>The number of chains used in the estimation process; `nchains` must be _\ge 2_</td>
 </tr>
 <tr valign="top">
  <td>`burnin`</td>
  <td>The number of discarded model iterations; defaults to 10,000</td>
 </tr>
 <tr valign="top">
  <td>`update`</td>
  <td>The number of withheld model iterations; defaults to 10,000</td>
 </tr>
 <tr valign="top">
  <td>`verbose`</td>
  <td>Logical flag, indicating if JAGS process output should be printed to the R console; defaults to `FALSE`</td>
 </tr>
</tbody>
</table>

### Details

`truePrevPools` calls on [**JAGS**](http://mcmc-jags.sourceforge.net/) via [**rjags**](https://cran.r-project.org/package=rjags) to estimate the true prevalence from the apparent prevalence in a Bayesian framework. The default model, in BUGS language, is given below. To see the actual fitted model, see the model slot of the `r doc("prev-class")` object.

```{r, eval=FALSE}
model {
    for (i in 1:N) {
      x[i] ~ dbern(AP[i])
      AP[i] <- SEpool[i] * (1 - pow(1 - TP, n[i])) + (1 - SPpool[i]) * pow(1 - TP, n[i])
      SEpool[i] <- 1 - (pow(1 - SE, n[i] * TP) * pow(SP, n[i] * (1 - TP)))
      SPpool[i] <- pow(SP, n[i])
    }
  # SE ~ user-defined
  # SP ~ user-defined
  TP ~ dbeta(prior[1], prior[2])
  }
```

The test sensitivity (`SE`) and specificity (`SP`) can be specified by the user, independently, as one of `"fixed"` (default), `"uniform"`, `"beta"`, `"pert"`, or `"beta-expert"`. Note that `SE` and `SP` must correspond to the test characteristics for testing individual samples; `truePrevPools` will calculate `SEpool` and `SPpool`, the sensitivity and specificitiy for testing pooled samples, based on [Boelaert et al. (2000)](#references).

Distribution parameters can be specified in a _named_ `list()` as follows:

*   **Fixed:** `list(dist = "fixed", par)`

*   **Uniform:** `list(dist = "uniform", min, max)`

*   **Beta:** `list(dist = "beta", alpha, beta)`

*   **PERT:** `list(dist = "pert", method, a, m, b, k)`  
    `'method'` must be `"classic"` or `"vose"`;  
    `'a'` denotes the pessimistic (minimum) estimate, `'m'` the most likely estimate, and `'b'` the optimistic (maximum) estimate;  
    `'k'` denotes the scale parameter.  
    See `r doc("betaPERT")` for more information on Beta-PERT parametrization.

*   **Beta-Expert:** `list(dist = "beta-expert", mode, mean, lower, upper, p)`  
    `'mode'` denotes the most likely estimate, `'mean'` the mean estimate;  
    `'lower'` denotes the lower bound, `'upper'` the upper bound;  
    `'p'` denotes the confidence level of the expert.  
    Only `mode` or `mean` should be specified; `lower` and `upper` can be specified together or alone.  
    See `r doc("betaExpert")` for more information on Beta-Expert parameterization.

For Uniform, Beta and Beta-PERT distributions, BUGS-style short-hand notation is also allowed:

*   **Uniform:** `~dunif(min, max)`

*   **Beta:** `~dbeta(alpha, beta)`

*   **Beta-PERT:** `~dpert(min, mode, max)`

### Value

An object of class `r doc("prev-class")`.

### Note

Markov chain Monte Carlo sampling in `truePrev` is performed by [**JAGS**](http://mcmc-jags.sourceforge.net/) (Just Another Gibbs Sampler) through the [**rjags**](https://cran.r-project.org/package=rjags) package. JAGS can be downloaded from http://sourceforge.net/projects/mcmc-jags/.

### References

* Speybroeck N, Williams CJ, Lafia KB, Devleesschauwer B, Berkvens D (2012) Estimating the prevalence of infections in vector populations using pools of samples. _Med Vet Entomol_ **26**:361-371. http://dx.doi.org/10.1111/j.1365-2915.2012.01015.x

* Boelaert F, Walravens K, Biront P, Vermeersch JP, Berkvens D, Godfroid J (2000) Prevalence of paratuberculosis (Johne's disease) in the Belgian cattle population. _Vet Microbiol_ **77**:269-281. http://dx.doi.org/10.1016/S0378-1135(00)00312-6

### See Also

[**coda**](https://cran.r-project.org/package=coda) for various functions that can be applied to the `prev@mcmc` object

`r doc("truePrev")`: estimate true prevalence from apparent prevalence obtained by testing _individual_ samples with a single test

`r doc("truePrevMulti")`: estimate true prevalence from apparent prevalence obtained by testing _individual_ samples with multiple tests, using a conditional probability scheme

`r doc("truePrevMulti2")`: estimate true prevalence from apparent prevalence obtained by testing _individual_ samples with multiple tests, using a covariance scheme

`r doc("betaPERT")`: calculate the parameters of a Beta-PERT distribution

`r doc("betaExpert")`: calculate the parameters of a Beta distribution based on expert opinion

### Examples

```{r}
## Sandflies in Aurabani, Nepal, 2007
pool_results <- c(0, 0, 0, 0, 0, 0, 0, 0, 1, 0)
pool_sizes <- c(2, 1, 6, 10, 1, 7, 1, 4, 1, 3)
```

```{r}
## Sensitivity ranges uniformly between 60% and 95%
## Specificity is considered to be 100%
```

```{r}
## .. BUGS-style
truePrevPools(x = pool_results, n = pool_sizes,
              SE = ~dunif(0.60, 0.95), SP = 1)
```

```{r}
## .. list-style
SE <- list(dist = "uniform", min = 0.60, max = 0.95)
truePrevPools(x = pool_results, n = pool_sizes,
              SE = SE, SP = 1)
```


```{r child="footer.Rmd"}
```
