---
output: bd::html_body
---

```{r, echo=FALSE, message=FALSE, warning=FALSE}
source("preamble.R")
```

## 'prev' class structure and methods

<br>Functions `r doc_fun("truePrev")`, `r doc_fun("truePrevPools")`, `r doc_fun("truePrevMulti")` and `r doc_fun("truePrevMulti2")` create objects of S4 class `prev`. Different methods are available for manipulating these objects.

### Slots

Objects of class `prev` are so-called `S4` objects. You can think of these objects as being formally defined lists. Instead of using the `$`-operator for accessing the different elements, which are called slots, the `@`-operator needs to be used. Objects of class `prev` contain the following four slots:

```{r, echo=FALSE, results='asis'}
arg_table(
  '@par' = "A list of input parameters.",
  '@model' = "The fitted Bayesian model, in BUGS language (and given `S3` class `prevModel`).",
  '@mcmc' = "A list, with one element per chain, of the simulated true prevalences (and sensitivities and specificities in the case of [`truePrevMulti`](?main=docs&sub=truePrevMulti) and [`truePrevMulti2`](?main=docs&sub=truePrevMulti2)).",
  '@diagnostics' = "A list with elements for the Deviance Information Criterion (`$DIC`), the Brooks-Gelman-Rubin statistic (`$BGR`), and in the case of [`truePrevMulti`](?main=docs&sub=truePrevMulti) and [`truePrevMulti2`](?main=docs&sub=truePrevMulti2), the Bayes-P statistic (`$bayesP`)"
  )
```

### General methods

#### print method

```{r, eval=FALSE}
print(x, conf.level = 0.95, dig = 3, ...)
```

```{r, echo=FALSE, results='asis'}
arg_table(
  x = "An object of class `prev`",
  conf.level = "Confidence level to be used in credibility interval",
  dig = "Number of decimal digits to print",
  ... = "Other arguments to pass to the `print` function"
  )
```  

The `print` method prints the mean, median, mode, standard deviation and credibility interval of the estimated true prevalence (and sensitivities and specificities, for prev objects created by `r doc_fun("truePrevMulti")` and `r doc_fun("truePrevMulti2")`). In addition, the Brooks-Gelman-Rubin statistic and corresponding upper confidence limit are printed, or the multivariate BGR statistic for prev objects created by `r doc_fun("truePrevMulti")` and `r doc_fun("truePrevMulti2")`. BGR values substantially above 1 indicate lack of convergence. For `prev` objects created by `r doc_fun("truePrevMulti")`, the Bayes-P statistic is also printed. Bayes-P should be as close to 0.5 as possible.

#### summary method

```{r, eval=FALSE}
summary(object, conf.level)
```

```{r, echo=FALSE, results='asis'}
arg_table(
  object = "An object of class `prev`",
  conf.level = "Confidence level to be used in credibility interval"
  )
``` 

The `summary` method returns the mean, median, mode, standard deviation, variance, credibility interval and number of samples for each chain separately and for all chains combined.

#### as.matrix method

```{r, eval=FALSE}
as.matrix(x, iters = FALSE, chains = FALSE)
```

```{r, echo=FALSE, results='asis'}
arg_table(
  x = "An object of class `prev`",
  iters = "Logical flag, indicating whether a column should be added for iteration number; defaults to `FALSE`",
  chains = "Logical flag, indicating whether a column should be added for chain number; defaults to `FALSE`"
  )
``` 

The `as.matrix` method converts objects of class `prev` to `matrix`.

#### plot method

```{r, eval=FALSE}
plot(x, y = NULL, ...)
```

```{r, echo=FALSE, results='asis'}
arg_table(
  x = "An object of class `prev`",
  y = "Which parameter to plot? Defaults to `NULL`",
  ... = "Other arguments to pass to the `plot` function"
  )
``` 

The `plot` method generates density, trace, Brooks-Gelman-Rubin and autocorrelation plots.

### Methods inherited from the [**coda**](https://cran.r-project.org/package=coda) package

#### densplot method

```{r, eval=FALSE}
densplot(x, exclude_fixed = TRUE, ...)
```

```{r, echo=FALSE, results='asis'}
arg_table(
  x = "An object of class `prev`",
  exclude_fixed = "Should fixed parameters be excluded from plotting? Defaults to `TRUE`",
  ... = "Other arguments to pass to the `densplot` function"
  )
``` 

Displays a plot of the density estimate for each variable in `x`, calculated by the `density` function.

#### traceplot method

```{r, eval=FALSE}
traceplot(x, exclude_fixed = TRUE, ...)
```

```{r, echo=FALSE, results='asis'}
arg_table(
  x = "An object of class `prev`",
  exclude_fixed = "Should fixed parameters be excluded from plotting? Defaults to `TRUE`",
  ... = "Other arguments to pass to the `traceplot` function"
  )
``` 

Displays a plot of iterations versus sampled values for each variable in the chain, with a separate plot per variable.

#### autocorr.plot method

```{r, eval=FALSE}
autocorr.plot(x, exclude_fixed = TRUE, chain = 1, ...)
```

```{r, echo=FALSE, results='asis'}
arg_table(
  x = "An object of class `prev`",
  exclude_fixed = "Should fixed parameters be excluded from plotting? Defaults to `TRUE`",
  chain = "Which chain to plot in `autocorr.plot`? Defaults to `1`",
  ... = "Other arguments to pass to the `autocorr.plot` function"
  )
``` 

Plots the autocorrelation function for each variable in each chain in `x`.

### Examples

```{r}
## Taenia solium cysticercosis in Nepal
SE <- list(dist = "uniform", min = 0.60, max = 1.00)
SP <- list(dist = "uniform", min = 0.75, max = 1.00)
TP <- truePrev(x = 142, n = 742, SE = SE, SP = SP)
```

```{r}
## Summarize estimates per chain
summary(TP)
```

```{r}
## Diagnostic plots
par(mfrow = c(2, 2))
plot(TP)
```

```{r, fig.height=3}
## Generic plots from package coda
par(mfrow = c(1, 3))
densplot(TP)

par(mfrow = c(1, 3))
traceplot(TP)

par(mfrow = c(1, 3))
gelman.plot(TP)

par(mfrow = c(1, 3))
autocorr.plot(TP)
```

```{r}
## Use 'str()' to see the structure of object TP
str(TP)
```

```{r}
## Every slot can be accessed using the '@' operator
slotNames(TP)
```

```{r}
## .. input parameters
TP@par
```

```{r}
## .. fitted model
TP@model
```

```{r}
## .. simulated TP, SE, SP
str(TP@mcmc)
```

```{r}
## .. convert simulated TP, SE, SP to matrix
head(as.matrix(TP))
```

```{r}
## .. DIC and BGR (and bayesP)
TP@diagnostics
```

```{r}
## TP@mcmc elements inherit from class 'mcmc.list' in coda package
## List all available methods for this class
methods(class = "mcmc.list")
```


```{r child="footer.Rmd"}
```
