---
output: bd::html_body
---

```{r, echo=FALSE, message=FALSE, warning=FALSE}
source("preamble.R")
```

## Calculate confidence intervals for prevalences and other proportions

### Description

The `propCI` function calculates five types of confidence intervals for proportions:

* Wald interval (= Normal approximation interval, asymptotic interval)
* Agresti-Coull interval (= adjusted Wald interval)
* Exact interval (= Clopper-Pearson interval)
* Jeffreys interval (= Bayesian interval)
* Wilson score interval

### Usage

```{r, eval=FALSE}
propCI(x, n, method = "all", level = 0.95, sortby = "level")
```

### Arguments

<table>
 <tr>
  <td>`x`</td>
  <td>Number of successes (positive samples)</td>
 </tr>
 <tr>
  <td>`n`</td>
  <td>Number of trials (sample size)</td>
 </tr>
 <tr>
  <td>`method`</td>
  <td>Confidence interval calculation method; see [details](#details)</td>
 </tr>
 <tr>
  <td>`level`</td>
  <td>Confidence level for confidence intervals</td>
 </tr>
 <tr>
  <td>`sortby`</td>
  <td>Sort results by `"level"` or `"method"`</td>
 </tr>
</table>

### Details

Five methods are available for calculating confidence intervals. For convenience, synonyms are allowed.

`"agresti.coull", "agresti-coull", "ac"`

$$\tilde{n} = n + z_{1-\frac{\alpha}{2}}^2$$
$$\tilde{p} = \frac{1}{\tilde{n}}(x + \frac{1}{2} z_{1-\frac{\alpha}{2}}^2)$$
$$\tilde{p} \pm z_{1-\frac{\alpha}{2}} \sqrt{\frac{\tilde{p}(1-\tilde{p})}{\tilde{n}}}$$
    
`"exact", "clopper-pearson", "cp"`

$$(Beta(\frac{\alpha}{2}; x, n - x + 1), Beta(1 - \frac{\alpha}{2}; x + 1, n - x))$$

`"jeffreys", "bayes"`

$$(Beta(\frac{\alpha}{2}; x + 0.5, n - x + 0.5), Beta(1 - \frac{\alpha}{2}; x + 0.5, n - x + 0.5))$$

`"wald", "asymptotic", "normal"`

$$p \pm z_{1-\frac{\alpha}{2}} \sqrt{\frac{p(1-p)}{n}}$$

`"wilson"`

$$\frac{p + \frac{z_{1-\frac{\alpha}{2}}^2}{2n} \pm z_{1-\frac{\alpha}{2}} \sqrt{\frac{p(1-p)}{n} + \frac{z_{1-\frac{\alpha}{2}}^2}{4n^2}}}{1 + \frac{z_{1-\frac{\alpha}{2}}^2}{n}}$$

### Value

Data frame with seven columns:

<table>
 <tr>
  <td>`x`</td>
  <td>Number of successes (positive samples)</td>
 </tr>
 <tr>
  <td>`n`</td>
  <td>Number of trials (sample size)</td>
 </tr>
 <tr>
  <td>`p`</td>
  <td>Proportion of successes (prevalence)</td>
 </tr>
 <tr>
  <td>`method`</td>
  <td>Confidence interval calculation method</td>
 </tr>
 <tr>
  <td>`level`</td>
  <td>Confidence level</td>
 </tr>
 <tr>
  <td>`lower`</td>
  <td>Lower confidence limit</td>
 </tr>
 <tr>
  <td>`upper`</td>
  <td>Upper confidence limit</td>
 </tr>
</table>

### Note

In case the observed prevalence equals 0% (ie, `x == 0`), an upper one-sided confidence interval is returned. In case the observed prevalence equals 100% (ie, `x == n`), a lower one-sided confidence interval is returned. In all other cases, two-sided confidence intervals are returned.

### Examples

```{r}
## All methods, 95% confidence intervals
propCI(x = 142, n = 742)
```

```{r}
## Wald-type 90%, 95% and 99% confidence intervals
propCI(x = 142, n = 742, method = "wald", level = c(0.90, 0.95, 0.99))
```


```{r child="footer.Rmd"}
```
