---
output: bd::html_body
---

```{r, echo=FALSE, message=FALSE, warning=FALSE}
source("preamble.R")
```

## Calculate the parameters of a Beta-PERT distribution

### Description

The Beta-PERT methodology allows to parametrize a generalized Beta distribution based on expert opinion regarding a pessimistic estimate (minimum value), a most likely estimate (mode), and an optimistic estimate (maximum value). The `betaPERT` function incorporates two methods of calculating the parameters of a Beta-PERT distribution, designated `"classic"` and `"vose"`.

### Usage

```{r, eval=FALSE}
betaPERT(a, m, b, k = 4, method = c("classic", "vose"))

## S3 method for class 'betaPERT'
print(x, conf.level = .95, ...)
## S3 method for class 'betaPERT'
plot(x, y, ...)
```

### Arguments

```{r, echo=FALSE, results='asis'}
arg_table(
  a = "Pessimistic estimate (Minimum value)",
  m = "Most likely estimate (Mode)",
  b = "Optimistic estimate (Maximum value)",
  k = "Scale parameter",
  method = "`\"classic\"` or `\"vose\"`; see [details](\\#details)",
  x = "Object of class `betaExpert`",
  y = "Currently ignored",
  conf.level = "Confidence level used in printing quantiles of resulting Beta-PERT distribution",
  ... = "ther arguments to pass to function `print` and `plot`"
)
```

### Details

The Beta-PERT methodology was developed in the context of Program Evaluation and Review Technique (PERT). Based on a pessimistic estimate (minimum value), a most likely estimate (mode), and an optimistic estimate (maximum value), typically derived through expert elicitation, the parameters of a Beta distribution can be calculated. The Beta-PERT distribution is used in stochastic modeling and risk assessment studies to reflect uncertainty regarding specific parameters.

Different methods exist in literature for defining the parameters of a Beta distribution based on PERT. The two most common methods are included in the `BetaPERT` function:

**Classic**

The standard formulas for mean, standard deviation, $\alpha$ and $\beta\$, are as follows

$$mean = (a + k*m + b) / (k + 2)$$

$$sd = (b - a) / (k + 2)$$

$$\alpha = { (mean - a) / (b - a) } * { (mean - a) * (b - mean) / sd^{2} - 1 } $$

$$\beta = \alpha * (b - mean) / (mean - a)$$

The resulting distribution is a 4-parameter Beta distribution: $\(Beta(\alpha, \beta, a, b)\)$.

**Vose**

[Vose (2000)](#references) describes a different formula for $\alpha\$:

$$(mean - a) * (2 * m - a - b) / { (m - mean) * (b - a) }$$

Mean and β are calculated using the standard formulas; as for the classical PERT, the resulting distribution is a 4-parameter Beta distribution: $Beta(\alpha, \beta, a, b)$.

Note: If $m = mean$, $\alpha$ is calculated as $1 + k/2$, in accordance with the [**mc2d**](http://cran.r-project.org/web/packages/mc2d/) package (see 'Note').

### Value

A list of class `"betaPERT"`:

```{r, echo=FALSE, results='asis'}
arg_table(
  alpha = "Parameter $\\alpha$ (shape1) of the Beta distribution",
  beta = "Parameter $\\beta$ (shape2) of the Beta distribution",
  a = "Pessimistic estimate (Minimum value)",
  m = "Most likely estimate (Mode)",
  b = "Optimistic estimate (Maximum value)",
  method = "Applied method"
)
```

Available generic functions for class `"betaPERT"` are `print` and `plot`.

### Note

The [**mc2d**](http://cran.r-project.org/package=mc2d) package provides the probability density function, cumulative distribution function, quantile function and random number generation function for the PERT distribution, parametrized by the `"vose"` method.

### References

* **Classic**: Malcolm DG, Roseboom JH, Clark CE, Fazar W (1959) Application of a technique for research and development program evaluation. _Oper Res_ **7**(5):646-669.

* **Vose**: David Vose. _Risk analysis, a quantitative guide, 2nd edition._ Wiley and Sons, 2000.

* [PERT distribution in _ModelRisk_ (Vose software)](http://vosesoftware.com/ModelRiskHelp/index.htm\#Distributions/Continuous_distributions/PERT_distribution.htm)

### See Also

`r doc_fun("betaExpert")` for modelling a standard Beta distribution based on expert opinion

### Examples

```{r}
## The value of a parameter of interest is believed to lie between 0 and 50
## The most likely value is believed to be 10
```

```{r}
## .. Classical PERT
betaPERT(a = 0, m = 10, b = 50, method = "classic")
```

```{r}
## .. Vose parametrization
betaPERT(a = 0, m = 10, b = 50, method = "vose")
```


```{r child="footer.Rmd"}
```
