---
output: bd::html_body
---

```{r, echo=FALSE, message=FALSE, warning=FALSE}
source("preamble.R")
```

## Calculate the parameters of a Beta distribution based on expert information

### Description

The `betaExpert` function fits a (standard) Beta distribution to expert opinion. The expert provides information on a best-guess estimate (mode or mean), and an uncertainty range:

*   The parameter value is with `p*100%` certainty greater than `lower`

*   The parameter value is with `p*100%` certainty smaller than `upper`

*   The parameter value lies with `p*100%` in between `lower` and `upper`

### Usage

```{r, eval=FALSE}
betaExpert(best, lower, upper, p = 0.95, method = "mode")

## S3 method for class 'betaExpert'
print(x, conf.level = .95, ...)
## S3 method for class 'betaExpert'
plot(x, y, ...)
```

### Arguments

```{r, echo=FALSE, results='asis'}
arg_table(
  best = "Best-guess estimate; see argument `method`",
  lower = "Lower uncertainty limit",
  upper = "Upper uncertainty limit",
  p = "Expert's certainty level",
  method = "Does best-guess estimate correspond to the `mode` or to the `mean`? Defaults to `mode`",
  x = "Object of class `betaExpert`",
  y = "Currently not implemented",
  conf.level = "Confidence level used in printing quantiles of resulting Beta distribution",
  ... = "Other arguments to pass to function `print` and `plot`"
)
```

### Details

The methodology behind the `betaExpert` function is presented by [Branscum et al. (2005)](#references) and implemented in the **BetaBuster** software, written by Chun-Lung Su.

The parameters of a standard Beta distribution are calculated based on a best-guess estimate and a (_p_)100% uncertainty range, defined by a lower and/or upper limit. The `betaExpert` function uses minimization (function `optimize`) to derive $\alpha$ and $\beta$ from this best guess and lower and/or upper limit. The resulting distribution is a standard 2-parameter Beta distribution: $Beta(\alpha, \beta)$.

### Value

A list of class `"betaExpert"`:

```{r, echo=FALSE, results='asis'}
arg_table(
  alpha = "Parameter $\\alpha$ (shape1) of the Beta distribution",
  beta = "Parameter $\\beta$ (shape2) of the Beta distribution"
)
```

The `print` method for `"betaExpert"` additionally calculates the mean, median, mode, variance and range of the corresponding Beta distribution.

### References

* Branscum AJ, Gardner IA, Johnson WO (2005) Estimation of diagnostic-test sensitivity and specificity through Bayesian modeling. _Prev Vet Med_ **68**:145-163. http://dx.doi.org/10.1016/j.prevetmed.2004.12.005

### See Also

Package [**rriskDistributions**](http://cran.r-project.org/package=rriskDistributions), which provides a collection of functions for fitting distributions to given data or by known quantiles.  

`r doc_fun("betaPERT")` for modelling a generalized Beta distribution based on expert opinion

### Examples

```{r, fig.height=4}
## Most likely value (mode) is 90%
## Expert states with 95% certainty that true value is larger than 70%
betaExpert(best = 0.90, lower = 0.70, p = 0.95)
plot(betaExpert(best = 0.90, lower = 0.70, p = 0.95))
```

```{r, fig.height=4}
## Most likely value (mode) is 0%
## Expert states with 95% certainty that true value is smaller than 40%
plot(betaExpert(best = 0, upper = 0.40, p = 0.95))
```

```{r, fig.height=4}
## Most likely value (mode) is 80%
## Expert states with 90% certainty that true value lies in between 40% and 90%
plot(betaExpert(best = 0.80, lower = 0.40, upper = 0.90, p = 0.90))
```

```{r, fig.height=4}
## Mean value is assumed to be 80%
## Expert states with 90% certainty that true value lies in between 40% and 90%
plot(betaExpert(best = 0.80, lower = 0.40, upper = 0.90, p = 0.90, method = "mean"))
```


```{r child="footer.Rmd"}
```
