---
output: bd::html_body
---

```{r, echo=FALSE, message=FALSE, warning=FALSE}
source("preamble.R")
```

## **prevalence** `r pkg` / download & installation

<br>The **prevalence** package provides Frequentist and Bayesian methods useful in prevalence assessment studies. Several methods are available for estimating True Prevalence (TP) from Apparent Prevalence (AP).

Version `r pkg` of the **prevalence** package is [available on CRAN](https://cran.r-project.org/package=prevalence). Source code of the development version is [on GitHub](https://github.com/brechtdv/prevalence).

This is how you can install the prevalence package in **R**:

* download and install the latest version of **R** via [cran.r-project.org](https://cran.r-project.org/)
* download and install **JAGS** via [mcmc-jags.sourceforge.net](http://mcmc-jags.sourceforge.net/)
* download and install the **prevalence** package via

<ul>
<li style="list-style-type: none;">
```{r, eval=FALSE}
install.packages("prevalence")
```
</li>
</ul>

Finally, to attach **prevalence** to your **R** session, simply run
```{r, eval=FALSE}
library(prevalence)
```

### Package description

```{r}
packageDescription("prevalence")
```


```{r child="footer.Rmd"}
```
