---
output: bd::html_body
---

```{r, echo=FALSE, message=FALSE, warning=FALSE}
source("preamble.R")
```

## **prevalence** `r pkg` / functions

<br><table>
 <tr valign="top">
  <td>`r doc_fun("propCI")`<td>
  <td>Derive confidence intervals for a prevalence estimate</td>
 </tr>
 <tr valign="top">
  <td>`r doc_fun("truePrev")`<td>
  <td>Estimate TP from AP obtained by testing individual samples with a single test</td>
 </tr>
 <tr valign="top">
  <td>`r doc_fun("truePrevPools")`<td>
  <td>Estimate TP from AP obtained by testing pooled samples</td>
 </tr>
 <tr valign="top">
  <td>`r doc_fun("truePrevMulti")`<td>
  <td>Estimate TP from AP obtained by testing individual samples with multiple tests, using a conditional probability scheme</td>
 </tr>
 <tr valign="top">
  <td>`r doc_fun("truePrevMulti2")`<td>
  <td>Estimate TP from AP obtained by testing individual samples with multiple tests, using a covariance scheme</td>
 </tr>
 <tr valign="top">
  <td>`r doc_fun("betaPERT")`<td>
  <td>Calculate the parameters of a Beta-PERT distribution</td>
 </tr>
 <tr valign="top">
  <td>`r doc_fun("betaExpert")`<td>
  <td>Calculate the parameters of a Beta distribution based on expert opinion</td>
 </tr>
</table>


```{r child="footer.Rmd"}
```
