---
output: bd::html_body
---

```{r, echo=FALSE, message=FALSE, warning=FALSE}
source("preamble.R")
```

## **prevalence** `r pkg` / functions

<table>
 <tr valign="top">
  <td>[`propCI`](?main=docs&sub=propCI)<td>
  <td>Derive confidence intervals for a prevalence estimate</td>
 </tr>
 <tr valign="top">
  <td>[`truePrev`](?main=docs&sub=truePrev)<td>
  <td>Estimate TP from AP obtained by testing individual samples with a single test</td>
 </tr>
 <tr valign="top">
  <td>[`truePrevMulti`](?main=docs&sub=truePrevMulti)<td>
  <td>Estimate TP from AP obtained by testing individual samples with multiple tests, using a conditional probability scheme</td>
 </tr>
 <tr valign="top">
  <td>[`truePrevMulti2`](?main=docs&sub=truePrevMulti2)<td>
  <td>Estimate TP from AP obtained by testing individual samples with multiple tests, using a covariance scheme</td>
 </tr>
 <tr valign="top">
  <td>[`truePrevPools`](?main=docs&sub=truePrevPools)<td>
  <td>Estimate TP from AP obtained by testing pooled samples</td>
 </tr>
 <tr valign="top">
  <td>[`betaPERT`](?main=docs&sub=betaPERT)<td>
  <td>Calculate the parameters of a Beta-PERT distribution</td>
 </tr>
 <tr valign="top">
  <td>[`betaExpert`](?main=docs&sub=betaExpert)<td>
  <td>Calculate the parameters of a Beta distribution based on expert opinion</td>
 </tr>
</table>


```{r child="footer.Rmd"}
```
